Out-of-Sample Comparisons of Overfit Models

### 2014-01-30 paper.tex
Clean up end of Lemma A5
This commit makes a few statements at the end of Lemma A5
explicit and closes #32.
Add definition of pseudo-true model parameters
This commit adds a definition of \theta_1 and \theta_2. This commit
closes #1.
Clear up confusing sentence about what the oos test *doesn't* measure
This commit tries to clear up a point of confusion for one of the
referees and closes #13

\subsection{Notation and Forecasting Environment}
We assume the following forecasting environment. There are two
competing linear models that give forecasts for the target,
$y_{t+\h}$:
\[
y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
\]
$t = 1,\dots,T-h$, $\h$ is the forecast horizon, and the
variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
Let
\begin{equation*}
  \mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)
\end{equation*}
with $x_t$ the vector of all elements of $x_{1t}$ and $x_{2t}$ after
removing duplicates, and let $\E_t$ and $\var_t$ denote the
conditional mean and variance given $\mathcal{F}_t$.  The first model
uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
generality, assume that $K_1 \leq K_2$.  We will allow $K_1$ and $K_2$
to vary with $T$, so a stochastic array underlies all of our
asymptotic theory, but we suppress that notation to simplify the
presentation.

@@

This result allows forecasters to use the \dmw\ test to conduct
inference about the models' accuracy.  Since the \oos\ average,
$\oosA$, is asymptotically normal and centered on the expected future
performance, $t$-tests constructed from the \oos\ errors necessarily
test hypotheses about $\E_T \oosB$ and not the performance of the
pseudo-true models or the unconditional performance of the models.
This application to testing can be expressed as its own theorem:
\begin{thm}\label{res:oostest}
Suppose that the conditions of Theorem \ref{res-confidence-intervals}
hold and that $\lim \Pr[\E_T \oosB \leq 0] > 0$.  Then
\begin{equation}
  \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
  \oosB \leq 0] \leq \alpha.
\end{equation}
\end{thm}

@@

Now define $D_s^*$, $s = R+1,\dots,T-\h$, as in Lemma
\ref{lem-basic-coupling} so that $\E_{s-1} D_s^* = \E_R D_s^*$ almost
surely.  Note that we also have the equality $\E_R D_s^* = \E_R
D_{R+1}^*$ almost surely for all $s\geq R+1$, and so
\[
P^{-1} \oosSum{s}{1} (\E_R D_s^*)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
D_s^*\Big)^2 \quad \text{a.s..}
\]

Consequently,
\begin{align*}
P^{-1} \oosSum{s}{1} (\E_R D_s)^2 - (\E_R\oosA)^2 & =
P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\\
&\quad+ \Big(P^{-1} \oosSum{s}{1} \E_R D_s^*\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\Big).
\end{align*}
Finally,
\begin{align*}
\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R D_s^*)^2] \Big\rVert_1
&\leq P^{-1} \oosSum{s}{1} \lVert \E_RD_s - \E_R D_s^* \rVert_2 \lVert
\E_RD_s + \E_R D_s^* \rVert_2
\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_RD_s - \E_R D_s^* \rVert_2,
\end{align*}
and this last term vanishes as in the proof of Lemma~\ref{lem:a2}.
\end{proof}

>>>>

\subsection{Notation and Forecasting Environment}
We assume the following forecasting environment. There are two
competing linear models that give forecasts for the target,
$y_{t+\h}$:
\[
y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
\]
$t = 1,\dots,T-h$, $\h$ is the forecast horizon, and the
variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
The coefficients $\theta_1$ and $\theta_2$ minimize the population
Mean Square Error, so
\begin{equation*}
  \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
\end{equation*}
making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$. Let
\begin{equation*}
  \mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)
\end{equation*}
with $x_t$ the vector of all elements of $x_{1t}$ and $x_{2t}$ after
removing duplicates, and let $\E_t$ and $\var_t$ denote the
conditional mean and variance given $\mathcal{F}_t$.  The first model
uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
generality, assume that $K_1 \leq K_2$.  We will allow $K_1$ and $K_2$
to vary with $T$, so a stochastic array underlies all of our
asymptotic theory, but we suppress that notation to simplify the
presentation.

@@

This result allows forecasters to use the \dmw\ test to conduct
inference about the models' accuracy.  Since the \oos\ average,
$\oosA$, is asymptotically normal and centered on the expected future
performance, $t$-tests constructed from the \oos\ errors necessarily
test hypotheses about $\E_T \oosB$ and not the performance of the
pseudo-true models or the unconditional performance of the
models.\footnote{i.e. $\E L(\e_{1,t+\h}) - \E  L(\e_{2,t+\h})$ or $\E \oosB$.
Note that the expectation of $\E_T \oosB$ equals $\E \oosB$ but that
$\sqrt{P} (\E_T \oosB - \E \oosB)$ may not be asymptotically normal,
which would be necessary for testing.}
This application to testing can be expressed as its own theorem:
\begin{thm}\label{res:oostest}
Suppose that the conditions of Theorem \ref{res-confidence-intervals}
hold and that $\lim \Pr[\E_T \oosB \leq 0] > 0$.  Then
\begin{equation}
  \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
  \oosB \leq 0] \leq \alpha.
\end{equation}
\end{thm}

@@

Now define $D_s^*$, $s = R+1,\dots,T-\h$, as in Lemma
\ref{lem-basic-coupling} so that $\E_{s-1} D_s^* = \E_R D_s^*$ almost
surely.  Note that we also have the equality $\E_R D_s^* = \E_R
D_{R+1}^*$ almost surely for all $s\geq R+1$, and so
\[
P^{-1} \oosSum{s}{1} (\E_R D_s^*)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
D_s^*\Big)^2 \quad \text{a.s.}
\]
Consequently,
\begin{align*}
P^{-1} \oosSum{s}{1}& (\E_R D_s)^2 - (\E_R\oosA)^2 \\
&= P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]
 + \Big(P^{-1} \oosSum{s}{1} \E_R D_s^*\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\Big)
 + O_p\Big(P^{-1} \oosSum{s}{1} \E_R (D_s - D_s^*)\Big).
\end{align*}
Finally,
\begin{align*}
\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R D_s^*)^2] \Big\rVert_1
&\leq P^{-1} \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2 \lVert
\E_R (D_s + D_s^*) \rVert_2
\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2,
\end{align*}
and this last term vanishes as in the proof of Lemma~\ref{lem:a2},
completing the proof.
\end{proof}
